Radiance - A Web Application Environment

### 2016-12-16 els2017-radiance/els2017-radiance.tex
Remove bib for now

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks\cite{microframeworks}, to a vast range of tools including database access, authentication, user management, validation, API endpoints, etc. All of the components exist with the aim of reducing the amount of work necessary to write a specific web application. \\

@@

\bibliography{els2017-radiance}
\end{document}

>>>>

A web application framework is comprised of several components. This can go from the absolute minimum of an HTTP server and URL dispatch mechanism as seen in microframeworks, to a vast range of tools including database access, authentication, user management, validation, API endpoints, etc. All of the components exist with the aim of reducing the amount of work necessary to write a specific web application. \\

@@

%\bibliography{els2017-radiance}
\end{document}
